Bandit Multiclass Linear Classification: Efficient Algorithms for the Separable Case

### 2019-01-22 ICML-submission/appendix-nearest-neighbor-algorithm.tex
Clean-ups

\begin{algorithm}
\caption{A nearest-neighbor algorithm for \textsc{Online Multiclass Linear Classification with
Bandit Feedback}}
\begin{algorithmic}[1]
\STATE $S \gets \emptyset$.
\FOR{$t=1,2,\ldots,T$:}
\IF{$\min_{(x,y) \in S} \| x_t - x \|_2 \leq \gamma$}
	\STATE $\hat{y}_t \gets \tilde{y}$, where $(\tilde{x}, \tilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}_2$.
\ELSE
	\STATE Predict $\hat{y}_t$ uniformly at random from $\cbr{1,2,\dots,K}$, receive feedback $z_t = \indicator{\hat{y}_t \neq y_t}$.
  \label{line:nn-explore}
	\IF{$z_t = 0$}
    \STATE $S \gets S \cup \cbr{(x_t, \hat{y}_t)}$.
  \ENDIF
\ENDIF
\ENDFOR
\end{algorithmic}
\label{alg:nn}
\end{algorithm}

We present Algorithm~\ref{alg:nn} in this section. The algorithm is based on the
following insight.

\begin{lemma}
Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly
separable examples. For $i$, $j$ in $\cbr{1,\ldots,T}$, if $x_i$ and $x_j$ have
$\ell_2$ distance at most $\gamma$, then $y_i = y_j$. \label{lem:nn}
\end{lemma}

\begin{proof}
Suppose for the sake on contradiction that $y_i \neq y_j$. By
Definition~\ref{definition:weak-linear-separability}, there exists a set of $k$
vectors $(w_1, \ldots, w_k)$, such that
Equations~\eqref{equation:weak-linear-separability-1}
and~\eqref{equation:weak-linear-separability-1} are satisfied.

Specifically,
\[ \ip{w_{y_i} - w_{y_j}}{x_i} \geq \gamma \]
\[ \ip{w_{y_j} - w_{y_i}}{x_j} \geq \gamma \]

This implies that
\[ \ip{w_{y_i} - w_{y_j}}{x_i - x_j} \geq 2\gamma \]

On the other hand,
\[ \ip{w_{y_i} - w_{y_j}}{x_i - x_j} \leq \| w_{y_i} - w_{y_j} \| \| x_i - x_j \| \leq \sqrt{2} \gamma \]
where the first inequality is from Cauchy-Schwarz,
the second inequality is from that
$\|w_{y_i} - w_{y_j}\| \leq \sqrt{2(\|w_{y_i}\|^2 + \|w_{y_j}\|^2)} \leq \sqrt{2}$ and our assumption
on $x_i$ and $x_j$. Therefore, we reach a contradiction.
\end{proof}

\begin{theorem}
\label{thm:margin_at_upper}
Suppose $(x_1,y_1), \ldots, (x_T, y_T)$ is a set of $\gamma$-weakly linearly
separable examples. In addition, for all $t$ in $\cbr{1,2,\dots,T}$, $\| x_t \|
\leq R$. Then, the expected number of mistakes made by Algorithm~\ref{alg:nn} is
such that \[\Exp[M] \le (K-1) (\frac R \gamma)^d. \]
\end{theorem}

\begin{proof}
Let $b_t$ be the indicator that line~\ref{line:nn-explore} is executed at
timestep $t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then
by Lemma~\ref{lem:nn}, the prediction $\hat{y}_t$ must equal $y_t$, i.e. $z_t =
0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$. Let $U =
\sum_{t=1}^T b_t (1-z_t)$; it can be seen that $U$ is the number of times when
$S$ gets updated. As $S$ is a $\gamma$-packing over $\cbr{x: \|x\|_2 \leq R}$,
the size of $S$ is at most $(\frac R \gamma)^d$, which is also an upper bound on
$U$.

Note that when $b_t = 1$, $\hat{y}_t$ is chosen uniformly at random, we have
\[ \Exp[ z_t | b_t = 1] = \frac{K-1}{K} \]
Therefore,
\[ \Exp[M] = \Exp[\sum_{t=1}^T b_t z_t] = \frac{K-1}{K} \Exp[\sum_{t=1}^T b_t]. \]
On the other hand,
\[ \Exp[U] = \Exp[\sum_{t=1}^T b_t (1-z_t)] = \frac 1 K \Exp[\sum_{t=1}^T b_t]. \]
Therefore,
\[ \Exp[M] = (K-1) \Exp[U] \leq (K-1) (\frac R \gamma)^d. \]
\end{proof}

>>>>

\begin{algorithm}[H]
\caption{\textsc{Nearest-Neighbor Algorithm}}
\begin{algorithmic}[1]
\REQUIRE{Number of classes $K$, number of rounds $T$.}
\REQUIRE{Inner product space $(V,\ip{\cdot}{\cdot})$.}
\STATE $S \gets \emptyset$.
\FOR{$t=1,2,\ldots,T$:}
\IF{$\min_{(x,y) \in S} \norm{x_t - x} \le \gamma$}
  \STATE{Find nearest neighbor \\ $(\widetilde{x}, \widetilde{y}) = \argmin_{(x,y) \in S} \norm{x_t - x}$}
	\STATE{Predict $\widehat{y}_t = \widetilde{y}$}
\ELSE
	\STATE{Predict $\widehat y_t \sim \text{Uniform}(\{1,2,\dots,K\})$}
	\STATE{Receive feedback $z_t = \indicator{\widehat{y}_t \neq y_t}$}
  \label{line:nearest-neighbor-explore}
	\IF{$z_t = 0$}
    \STATE $S \gets S \cup \cbr{(x_t, \widehat{y}_t)}$.
  \ENDIF
\ENDIF
\ENDFOR
\end{algorithmic}
\label{algorithm:nearest-neighbor}
\end{algorithm}

In this section we analyze \textsc{Nearest-Neighbor Algorithm} shown as
Algorithm~\ref{algorithm:nearest-neighbor}. The algorithm is based on the idea
that two examples that are close to each other must have the same label. Lemma
below formalizes this intuition.

\begin{lemma}
\label{lemma:nearest-neighbor}
Let $(V,\ip{\cdot}{\cdot})$ be a vector space, $K$ be a positive integer and let
$\gamma$ be a positive real number. Suppose $(x_1,y_1), (x_2,y_2), \dots, (x_T,
y_T) \in V \times \{1,2,\dots,K\}$ are labeled examples that are weakly linearly
separable with margin $\gamma$. For $i$, $j$ in $\cbr{1,2,\dots,T}$, if
$\norm{x_i - x_j}_2 \le \gamma$ then $y_i = y_j$.
\end{lemma}

\begin{proof}
Suppose for the sake on contradiction that $y_i \neq y_j$. By
Definition~\ref{definition:linear-separability}, there exists a set of $k$
vectors $(w_1, \ldots, w_k)$, such that
conditions~\eqref{equation:weak-linear-separability-1}
and~\eqref{equation:weak-linear-separability-2} are satisfied.

Specifically,
\begin{align*}
\ip{w_{y_i} - w_{y_j}}{x_i} & \ge \gamma \; , \\
\ip{w_{y_j} - w_{y_i}}{x_j} & \ge \gamma \; .
\end{align*}
This implies that
$$
\ip{w_{y_i} - w_{y_j}}{x_i - x_j} \ge 2\gamma \; .
$$

On the other hand,
$$
\ip{w_{y_i} - w_{y_j}}{x_i - x_j} \le \norm{w_{y_i} - w_{y_j}} \cdot \norm{x_i - x_j} < \sqrt{2} \gamma
$$
where the first inequality is from Cauchy-Schwartz inequality, the second
inequality is from that $\norm{w_{y_i} - w_{y_j}} \le \sqrt{2(\norm{w_{y_i}}^2 +
\norm{w_{y_j}}^2)} \leq \sqrt{2}$ and our assumption on $x_i$ and $x_j$.
Therefore, we reach a contradiction.
\end{proof}

\begin{theorem}
\label{theorem:margin_at_upper}
Let $K$ and $d$ be positive integers and let $\gamma$ be a positive real number.
Suppose $(x_1,y_1), \ldots, (x_T, y_T) \in \R^d \times \{1,2,\dots,K\}$ are
labeled examples that are weakly linearly separable with margin $\gamma$ and
satisfy $\norm{x_1}, \norm{x_2}, \dots, \norm{x_T} \le R$. Then, the expected
number of mistakes made by Algorithm~\ref{algorithm:nearest-neighbor} is at most
$$
(K-1) \left( \frac{R}{\gamma} \right)^d \; .
$$
\end{theorem}

\begin{proof}
Let $M$ be the number of mistakes made by the algorithm. Let $b_t$ be the
indicator that line~\ref{line:nearest-neighbor-explore} is executed at timestep
$t$, i.e. we fall into the ``else'' case. Note that if $b_t = 0$, then by
Lemma~\ref{lemma:nearest-neighbor}, the prediction $\widehat{y}_t$ must equal
$y_t$, i.e. $z_t = 0$. Therefore, $M = \sum_{t=1}^T z_t = \sum_{t=1}^T b_t z_t$.
Let $U = \sum_{t=1}^T b_t (1-z_t)$. Clearly, $|S| = U$. Since $S$ is a
$\gamma$-packing over $\cbr{x \in \R^d ~:~ \norm{x} \le R}$, the size of $S$ is
at most $(\frac R \gamma)^d$, which is also an upper bound on $U$.

Note that when $b_t = 1$, $\widehat{y}_t$ is chosen uniformly at random, we have
$$
\Exp[ z_t | b_t = 1] = \frac{K-1}{K} \; .
$$
Therefore,
$$
\Exp[M] = \Exp \left[ \sum_{t=1}^T b_t z_t \right] = \frac{K-1}{K} \Exp \left[ \sum_{t=1}^T b_t \right] \; .
$$
On the other hand,
$$
\Exp[U] = \Exp \left[ \sum_{t=1}^T b_t (1-z_t) \right] = \frac 1 K \Exp \left[\sum_{t=1}^T b_t \right] \; .
$$
Therefore,
$$
\Exp[M] = (K-1) \Exp[U] \leq (K-1) \left(\frac{R}{\gamma} \right)^d \; .
$$
\end{proof}

### 2019-01-22 ICML-submission/appendix-proofs-for-strongly-separable-examples.tex
Clean-ups

Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
\endgroup
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:weak-linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
then $\widehat y_t \neq y_t$, by
Equation~\eqref{equation:strong-linear-separability-3}, we have that
$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.

>>>>

Hence, after $U$ updates,
\begin{equation}
\sum_{i=1}^K \norm{w_i^{(T+1)}}^2 \le R^2 U \; .
\label{eqn:norm-ub}
\end{equation}
Similarly, if there is an update in round $t$, we have
\begingroup
\allowdisplaybreaks
\begin{align*}
& \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t+1)}} \\
& = \left( \sum_{i \in \{1,2,\dots,K\} \setminus \{\widehat y_t\}} \ip{w_i^*}{w_i^{(t)}} \right) \\
& \qquad + \ip{w_{\widehat y_t}^*}{w_{\widehat y_t}^{(t)} + (-1)^{z_t} x_t} \\
& = \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + (-1)^{z_t} \ip{w_{\widehat y_t}^*}{x_t} \\
& \ge \left( \sum_{i=1}^K \ip{w_i^*}{w_i^{(t)}} \right) + \frac \gamma 2,
\end{align*}
\endgroup
where the last inequality follows from a case analysis on $z_t$ and
Definition~\ref{definition:linear-separability}: if $z_t = 0$, then
$\widehat y_t = y_t$, by Equation~\eqref{equation:strong-linear-separability-2},
we have that $\ip{w_{\widehat y_t}^*}{x_t} \geq \frac \gamma 2$; if $z_t = 1$,
then $\widehat y_t \neq y_t$, by
Equation~\eqref{equation:strong-linear-separability-3}, we have that
$\ip{w_{\widehat y_t}^*}{x_t} \le -\frac \gamma 2$.

### 2019-01-22 ICML-submission/introduction.tex
Clean-ups

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between a learner and an adversary. At each
timestep $t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in \R^d$ to the learner.  
Upon receiving $x_t$, the learner makes a prediction $\widehat{y}_t$ and receives feedback. 
In contrast to the
standard full-information setting, where the feedback given is the correct label
$y_t$, here the feedback is only a binary indicator of whether the prediction
was correct or not. The protocol of the problem is formally stated below.

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
\For{$t=1,2,\dots,T$}{
     Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
     Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
     Observe feedback
          $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
%$z_t \in \{0,1\}$, \\ \qquad where $z_t = \begin{cases}
%0 & \text{if $\widehat y_t = y_t$,} \\
%1 & \text{if $\widehat y_t \neq y_t$.}
%\end{cases}$
}

\end{protocol}

@@

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
two notions of linear separability, \emph{weak} and \emph{strong}, formally
stated in
Definition~\ref{definition:weak-linear-separability}.
The standard notion of multiclass linear
separability~\citep{Crammer-Singer-2003} corresponds to the weak linear
separability. %For binary classification, the weak and strong separability are
%identical. However, they differ for multiclass classification with $K \ge 3$
%classes. 
For multiclass classification with $K$ classes, weak linear
separability requires that all examples from the same class lie in an intersection of $K-1$ halfspaces and all other examples lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane.

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes.
%%%%%
It is also known that any (possibly randomized) algorithm must
make $\frac{1}{2} \left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the
worst case.
The \textsc{Multiclass Perceptron} achieves an
information-theoretically optimal mistake bound, while being
computationally and memory efficient.
~\footnote{
%%%%%
%These are folklore results. 
For completeness, we present these 
folklore
%%%%%
results along
with their proofs in Appendix~\ref{section:multiclass-perceptron-proofs} in the
supplementary material.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: first, their Theorem 2
implies a mistake upper bound of $\frac{R}{\gamma}$ with
sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit
setting, as the algorithm only makes updates on a subset of the $w_i$'s.} We
design a simple and efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

For the case when the examples are weakly linearly separable, it was open for a long 
time whether there exist \textit{efficient} algorithms with finite mistake 
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}. 
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
is there \textit{any} algorithm with a finite mistake bound that has no explicit dependence 
on the dimensionality of the feature vectors? We answer both questions affirmatively by
providing an efficient algorithm with finite dimensionless mistake bound 
(Algorithm~\ref{algorithm:kernelized}) (Note: the second question was previously 
answered by~\cite{Daniely-Helbertal-2013} with an inefficient algorithm).

@@

>>>>

We study the problem of \textsc{Online Multiclass Linear Classification with
Bandit Feedback}~\citep{Kakade-Shalev-Shwartz-Tewari-2008}. The problem can be
viewed as a repeated game between a learner and an adversary. At each timestep
$t$, the adversary chooses a labeled example $(x_t, y_t)$ and reveals $x_t\in
\R^d$ to the learner. Upon receiving $x_t$, the learner makes a prediction
$\widehat{y}_t$ and receives feedback. In contrast with the standard
full-information setting, where the feedback given is the correct label $y_t$,
here the feedback is only a binary indicator of whether the prediction was
correct or not. The protocol of the problem is formally stated below.

\begin{protocol}[h]
\caption{\textsc{Online Multiclass Linear Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\textbf{Require:} Number of classes $K$, number of rounds $T$.\\
\For{$t=1,2,\dots,T$}{
Adversary chooses example $(x_t, y_t)$, where $x_t$ is revealed to the learner.\\
Predict class label $\widehat y_t \in \{1,2,\dots,K\}$.\\
Observe feedback $z_t = \indicator{\widehat y_t \neq y_t} \in \{0,1\}$
}
\end{protocol}

@@

In this paper, we focus on the special case when the examples chosen by the
adversary lie in $\R^d$ and are linearly separable with a margin. We introduce
two notions of linear separability, \emph{weak} and \emph{strong}, formally
stated in \autoref{definition:linear-separability}. The standard notion of
multiclass linear separability~\citep{Crammer-Singer-2003} corresponds to the
weak linear separability. For multiclass classification with $K$ classes, weak
linear separability requires that all examples from the same class lie in an
intersection of $K-1$ halfspaces and all other examples lie in the complement of
the intersection of the halfspaces. Strong linear separability means that
examples from each class are separated from the remaining examples by a
\emph{single} hyperplane.

In the full-information feedback setting, it is well known
\citep{Crammer-Singer-2003} that if all examples have norm at most $R$ and are
weakly linearly separable with a margin $\gamma$, then the \textsc{Multiclass
Perceptron} algorithm makes at most $\lfloor 2(R/\gamma)^2 \rfloor$ mistakes. It
is also known that any (possibly randomized) algorithm must make $\frac{1}{2}
\left\lfloor (R/\gamma)^2 \right \rfloor$ mistakes in the worst case. The
\textsc{Multiclass Perceptron} achieves an information-theoretically optimal
mistake bound, while being computationally and memory efficient.~\footnote{For
completeness, we present these folklore results along with their proofs in
Appendix~\ref{section:multiclass-perceptron-proofs} in the supplementary
material.}

The bandit feedback setting, however, is much more challenging. For the case
when the examples are strongly linearly separable, to the best of our knowledge,
it is not known how to design an efficient algorithm with a finite mistake bound
before our work.~\footnote{Although~\cite{Chen-Chen-Zhang-Chen-Zhang-2009}
claimed that their Conservative OVA algorithm with PA-I update has a finite
mistake bound under the strong linear separability condition, their proof of
Theorem 2 is incorrect: first, their Theorem 2 implies a mistake upper bound of
$\frac{R}{\gamma}$ with sufficiently large $C$, which contradicts our lower
bound in Theorem~\ref{theorem:strongly-separable-examples-mistake-lower-bound};
second, their Lemma 4 cannot be directly applied to the bandit setting, as the
algorithm only makes updates on a subset of the $w_i$'s.} We design a simple and
efficient algorithm
(Algorithm~\ref{algorithm:algorithm-for-strongly-linearly-separable-examples})
that makes at most $O(K (R/\gamma)^2))$ mistakes in expectation. Its memory
complexity and per-round time complexity are both $O(dK)$. The algorithm can be
viewed as running $K$ copies of the \textsc{Binary Perceptron} algorithm, one
copy for each class. We prove that any (possibly randomized) algorithm must make
$\Omega(K (R/\gamma)^2))$ mistakes in the worst case. The extra $O(K)$
multiplicative factor in the mistake bound, as compared to the full-information
setting, is the price we pay for the bandit feedback, or more precisely, the
lack of full-information feedback.

For the case when the examples are weakly linearly separable, it was open for a
long time whether there exist \textit{efficient} algorithms with finite mistake
bound~\cite{Kakade-Shalev-Shwartz-Tewari-2008, Beygelzimer-Orabona-Zhang-2017}.
Furthermore, in~\cite{Kakade-Shalev-Shwartz-Tewari-2008}, they ask the question:
Is there \textit{any} algorithm with a finite mistake bound that has no explicit
dependence on the dimensionality of the feature vectors? We answer both
questions affirmatively by providing an efficient algorithm with finite
dimensionless mistake bound (Algorithm~\ref{algorithm:kernelized}).\footnote{An
in inefficient algorithm was given by~\cite{Daniely-Helbertal-2013}.}

@@

In Appendix~\ref{section:nearest-neighbor-algorithm}, we propose a very
different algorithm that is based on the obvious idea that two points that are
close enough must have the same label. Here, close enough means that they cannot
be separated from each other by a linear separator with a margin.

### 2019-01-22 ICML-submission/notions-of-linear-separability.tex
Clean-ups

\begin{definition}
[Linear separability]
\label{definition:weak-linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number. 
We say that labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are 
%said to be
\begin{enumerate}
\item
\emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; ,
\end{gathered}
\end{align}
\item
\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma/2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \gamma/2 \; .
\end{gathered}
\end{align}
\end{enumerate}
\end{definition}

>>>>

\begin{definition}
[Linear separability]
\label{definition:linear-separability}
Let $(V,\ip{\cdot}{\cdot})$ be an inner product space, $K$ be a positive
integer, and $\gamma$ be a positive real number.
We say that labeled examples $(x_1, y_1),
(x_2, y_2), \dots, (x_T, y_T) \in V \times \{1,2,\dots,K\}$ are
%said to be
\begin{enumerate}
\item
\emph{weakly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:weak-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:weak-linear-separability-2}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_{y_t}} \ge \ip{x_t}{w_i} + \gamma \; ,
\end{gathered}
\end{align}
\item
\emph{strongly linearly separable with a margin $\gamma$} if there exist vectors
$w_1, w_2, \dots, w_K \in V$ such that
\begin{align}
\label{equation:strong-linear-separability-1}
& \sum_{i=1}^K \norm{w_i}^2 \le 1 \; , \\
\label{equation:strong-linear-separability-2}
& \forall t \in \{1,2,\dots,T\} \qquad \qquad \ip{x_t}{w_{y_t}} \ge \gamma/2 \; , \\
\label{equation:strong-linear-separability-3}
& \begin{gathered}
\forall t \in \{1,2,\dots,T\} \quad \forall i \in \{1,2,\dots, K\} \setminus \{y_t\} \\
\ip{x_t}{w_i} \le - \gamma/2 \; .
\end{gathered}
\end{align}
\end{enumerate}
\end{definition}
